Physcraper: a python package for continual update of evolutionary estimates using the Open Tree of Life

### 2020-08-28 methods-extended.Rmd
extended methods

---
output:
  html_document:
    keep_md: yes
    toc: false
geometry: margin = 1in
bibliography: paper.bib
csl: submission-mee/methods-in-ecology-and-evolution.csl
# csl: submission_sysbio/systematic-biology.csl
link-citations: yes
linestretch: 2
---

>>>>

---
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
  html_document:
    keep_md: yes
geometry: margin = 1in
bibliography: paper.bib
csl: submission-mee/methods-in-ecology-and-evolution.csl
# csl: submission_sysbio/systematic-biology.csl
link-citations: yes
linestretch: 2
---
